Hierarchical wrinkling in a confined permeable biogel

### 2015-05-15 fig_plis/article_SI.tex
Results and discussion avec 4 subsections

\paragraph*{Significance statement}
Confined thin surfaces may wrinkle due the growth of an excess of material. Here we present benchmark experiments that explore the possibility of wrinkling in biogels. We relate the excess area to the microstructural dynamics of the biogel. Usually the wrinkling wavelength is set by elasticity or gravity. In our case the wavelength is controlled by viscous flow, either in a lubrication layer or through the pores of the gel. Our results pave the way for exploring the possibility of wrinkling in porous soft materials floating in a liquid such as biological tissues: during morphogenesis of the embryo the development of confined permeable and wrinkled surface is ubiquitous.

@@

\section*{Dynamics of the wrinkling process}

@@

\section*{Syn\ae{}resis and swelling back mechanism}

@@

\section*{Wavelength selection mechanism}

@@

\section*{Experimental tests}

@@

\section*{Methods summary}

>>>>

%\paragraph*{Significance statement}
%Confined thin surfaces may wrinkle due the growth of an excess of material. Here we present benchmark experiments that explore the possibility of wrinkling in biogels. We relate the excess area to the microstructural dynamics of the biogel. Usually the wrinkling wavelength is set by elasticity or gravity. In our case the wavelength is controlled by viscous flow, either in a lubrication layer or through the pores of the gel. Our results pave the way for exploring the possibility of wrinkling in porous soft materials floating in a liquid such as biological tissues: during morphogenesis of the embryo the development of confined permeable and wrinkled surface is ubiquitous.

@@

\section*{Results and discussion}

\subsection*{Dynamics of the wrinkling process}

@@

\subsection*{Syn\ae{}resis and swelling back mechanism}

@@

\subsection*{Wavelength selection mechanism}

@@

\subsection*{Experimental tests}

@@

\section*{Materials and Methods}
